\LARGE \bf \pyRobots, a toolkit for robot executive control

### 2014-09-03 paper.tex
Mean and SD age of kindergarten expe

We brought two Ranger robots to a kindergarten (17 children, 3 to 4 years old),
and after a brief introduction (showing them that removing the pacifier would
``wake up'' the robot, and putting it back would make it ``fall asleep''), we
invited the children to freely play with the robots and integrate them into
their usual games. The experiment lasted 68 minutes.

>>>>

We brought two Ranger robots to a kindergarten (17 children, mean age: 3.88
years old, SD=0.65), and after a brief introduction (showing them that removing
the pacifier would ``wake up'' the robot, and putting it back would make it
``fall asleep''), we invited the children to freely play with the robots and
integrate them into their usual games. The experiment lasted 68 minutes.
